---
title: "ZetaVIEW Endosome Analysis"
author:
  - name: "Emir Turkes [emir.turkes.19@ucl.ac.uk] and Lizzie Glennon [lizzie.glennon@ucl.ac.uk]"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
link-citations: true
output:
  html_document:
    code_folding: hide
    number_sections: true
    theme: lumen
    highlight: haddock
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(
    inputFile,
    encoding = encoding,
    output_file = file.path("..", "results", "zetaview-endosome-analysis.html")
  )})
---

<style type="text/css">
body {font-size: 16px;}
h1.title {font-size: 35px;}
h1 {font-size: 24px;}
h2 {font-size: 22px;}
h3 {font-size: 20px;}
.toc-content {padding-left: 0px; padding-right: 0px;}
div.tocify {width: 100%;}
.tocify-subheader .tocify-item {font-size: 0.95em; padding-left: 25px; text-indent: 0;}
.tocify-subheader .tocify-subheader .tocify-item {
  font-size: 0.95em; padding-left: 35px; text-indent: 0;
}
div.main-container {max-width: none; width: 100%;}
</style>

*This file is a part of [ZetaVIEW Endosome Analysis](https://github.com/eturkes/zetaview-endosome-analysis).*

Analysis of endosome size using ZetaVIEW.

R code used in each section can be expanded with the CODE button at the right.  
Toggling the first CODE button at the start of the document enables showing and hiding of all code.

```{r}
# Load in necessary boilerplate and libraries.
# --------------------------------------------

#    This file is part of zetaview-endosome-analysis.
#    Copyright (C) 2021  Emir Turkes, Lizzie Glennon, UK DRI at UCL
#
#    This program is free software: you can redistribute it and/or modify
#    it under the terms of the GNU General Public License as published by
#    the Free Software Foundation, either version 3 of the License, or
#    (at your option) any later version.
#
#    This program is distributed in the hope that it will be useful,
#    but WITHOUT ANY WARRANTY; without even the implied warranty of
#    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
#    GNU General Public License for more details.
#
#    You should have received a copy of the GNU General Public License
#    along with this program.  If not, see <http://www.gnu.org/licenses/>.
#
#    Emir Turkes can be contacted at emir.turkes@eturkes.com

packages <- c(
  "conflicted", "RColorBrewer", "reshape2", "ggplot2", "MASS", "multidplyr", "fitdistrplus",
  "dplyr", "DT"
)
invisible(suppressPackageStartupMessages(lapply(packages, library, character.only = TRUE)))
source("utils.R")

colors <- c(brewer.pal(9, "Blues")[c(2, 4, 6, 8)], brewer.pal(9, "Reds")[c(2, 4, 6, 8)])

cluster <- new_cluster(4)
cluster_library(cluster, "fitdistrplus")
cluster_assign(cluster, avg_finder = avg_finder)

knitr::opts_chunk$set(dpi = 300)
# --------------------------------------------
```

# Prep

```{r}
data <- read.delim(file.path("..", "assets", "size-by-number.tsv"))

non_zero <- which(rowSums(data[ , -1]) > 0)
data <- data[min(non_zero):max(non_zero), ]

molten_data <- melt(data[ , -1], id.vars = NULL)
colnames(molten_data) <- c("sample", "frequency")
molten_data$size <- rep(data$size, ncol(data) - 1)
```

# Distribution Plots

## Smoothed

```{r}
ggplot(molten_data, aes(size, frequency, color = sample)) +
  geom_smooth(span = 0.1) +
  scale_color_manual(values = colors) +
  theme_light()
```

## Without Smoothing

```{r}
ggplot(molten_data, aes(size, frequency, color = sample)) +
  geom_line() +
  scale_color_manual(values = colors) +
  theme_light()
```

# Statistical Testing

```{r}
molten_data$group <- c(
  rep("APOE3", times = nrow(molten_data) / 2), rep("APOE4", times = nrow(molten_data) / 2)
)
molten_data$sex <- rep(
  c(rep("male", times = nrow(molten_data) / 4), rep("female", times = nrow(molten_data) / 4)),
  times = 2
)
```

## Poisson GLM

```{r}
model <- glm(frequency ~ group + sex + group:sex, poisson, molten_data)
summary(model)
```

### Goodness-of-fit

```{r}
1 - pchisq(summary(model)$deviance, summary(model)$df.residual)
```

## Negative Binomial GLM

```{r}
model <- glm.nb(frequency ~ group + sex + group:sex, molten_data)
summary(model)
```

### Goodness-of-fit

```{r}
1 - pchisq(summary(model)$deviance, summary(model)$df.residual)
```

### Further Results

```{r}
ranged_data <- molten_data[, -3]
ranged_data$left <- molten_data$size - 1.5
ranged_data$right <- molten_data$size + 1.5

nb_data <- ranged_data %>%
  group_by(sample) %>%
  partition(cluster = cluster) %>%
  do(neg_binomial_avg = avg_finder(.)) %>%
  collect() %>%
  mutate(neg_binomial_avg = unlist(neg_binomial_avg))

datatable_download(nb_data)
```

# References

This is the concluding section of the document.
Here we output the `sessionInfo` and create a bibliography for works cited.

```{r}
sessionInfo()
```
