---
title: "ZetaVIEW Endosome Analysis"
author:
  - name: "Emir Turkes [emir.turkes.19@ucl.ac.uk] and Lizzie Glennon [lizzie.glennon@ucl.ac.uk]"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
link-citations: true
output:
  html_document:
    code_folding: hide
    number_sections: true
    theme: lumen
    highlight: haddock
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(
    inputFile,
    encoding = encoding,
    output_file = file.path("..", "results", "zetaview-endosome-analysis.html")
  )})
---

<style type="text/css">
body {font-size: 16px;}
h1.title {font-size: 35px;}
h1 {font-size: 24px;}
h2 {font-size: 22px;}
h3 {font-size: 20px;}
.toc-content {padding-left: 0px; padding-right: 0px;}
div.tocify {width: 100%;}
.tocify-subheader .tocify-item {font-size: 0.95em; padding-left: 25px; text-indent: 0;}
.tocify-subheader .tocify-subheader .tocify-item {
  font-size: 0.95em; padding-left: 35px; text-indent: 0;
}
div.main-container {max-width: none; width: 100%;}
</style>

*This file is a part of [ZetaVIEW Endosome Analysis](https://github.com/eturkes/zetaview-endosome-analysis).*

Analysis of endosome size using ZetaVIEW.

R code used in each section can be expanded with the CODE button at the right.  
Toggling the first CODE button at the start of the document enables showing and hiding of all code.

```{r}
# Load in necessary boilerplate and libraries.
# --------------------------------------------

# Copyright 2021 Emir Turkes, Lizzie Glennon
# 
# Licensed under the Apache License, Version 2.0 (the "License");
# you may not use this file except in compliance with the License.
# You may obtain a copy of the License at
# 
#     http://www.apache.org/licenses/LICENSE-2.0
# 
# Unless required by applicable law or agreed to in writing, software
# distributed under the License is distributed on an "AS IS" BASIS,
# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
# See the License for the specific language governing permissions and
# limitations under the License.

packages <- c("conflicted", "RColorBrewer", "reshape2", "ggplot2")
invisible(suppressPackageStartupMessages(lapply(packages, library, character.only = TRUE)))

colors <- c(brewer.pal(9, "Blues")[c(2, 4, 6, 8)], brewer.pal(9, "Reds")[c(2, 4, 6, 8)])

knitr::opts_chunk$set(dpi = 300)
# --------------------------------------------
```

# Prep

```{r}
data <- read.delim(file.path("..", "assets", "size-by-number.tsv"))

non_zero <- which(rowSums(data[ , -1]) > 0)
data <- data[min(non_zero):max(non_zero), ]

molten_data <- melt(data[ , -1], id.vars = NULL)
colnames(molten_data) <- c("sample", "frequency")
molten_data$size <- rep(data$size, ncol(data) - 1)
```

# Distribution Plots

## Smoothed

```{r}
ggplot(molten_data, aes(size, frequency, color = sample)) +
  geom_smooth(span = 0.1) +
  scale_color_manual(values = colors) +
  theme_light()
```

## Without Smoothing

```{r}
ggplot(molten_data, aes(size, frequency, color = sample)) +
  geom_line() +
  scale_color_manual(values = colors) +
  theme_light()
```

# References

This is the concluding section of the document.
Here we output the `sessionInfo` and create a bibliography for works cited.

```{r}
sessionInfo()
```
